Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-12-10 .output/_tex/manuscript.tex

In table~\ref{tbl-midline-params}, we tabulate the mean and standard
deviation of the sampled parameters. The bilateral model mostly
reproduces the ipsilateral spread parameter values reported in the
earlier publication on the unilateral model
\citep{ludwig_modelling_2023}. Any discrepancies may be due to
differences in the patient cohorts. Therefore, we omit the analysis of
the ipsilateral spread patterns and focus instead on the analysis of
contralateral involvement. The small contralateral spread parameters
\(b^c_v\) compared to the ipsilateral parameters \(b^i_v\) adequately
reflect the low prevalence of contralateral lymph node involvement for
lateralized tumors. The mixing parameter \(\alpha=\) 0.3 describes that
the probability of contralateral spread is higher for tumors extending
over the mid-sagittal plane, but still lower than the probability for
ipsilateral spread.

The high value of \(t_{23}\) (0.1) compared to the value of \(b_3\)
(0.3) shows that the ipsilateral LNL III is rarely involved without the
upstream involvement of LNL II.

>>>>

In table~\ref{tbl-midline-params}, we tabulate the mean and standard
deviation of the sampled parameters. The bilateral model mostly
reproduces the ipsilateral spread parameter values reported in the
earlier publication on the unilateral model
\citep{ludwig_modelling_2023}. Any discrepancies may be due to
differences in the patient cohorts. Therefore, we omit the analysis of
the ipsilateral spread patterns and focus instead on the analysis of
contralateral involvement. The small contralateral spread parameters
\(b^c_v\) compared to the ipsilateral parameters \(b^i_v\) adequately
reflect the low prevalence of contralateral lymph node involvement for
lateralized tumors. The mixing parameter \(\alpha\) (33.9\%) describes
that the probability of contralateral spread is higher for tumors
extending over the mid-sagittal plane, but still lower than the
probability for ipsilateral spread.

The high value of \(t_{23}\) (14.2\%) compared to the value of
\(b_3^\text{i}\) (5.5\%) shows that the ipsilateral LNL III is rarely
involved without the upstream involvement of LNL II.

### 2024-12-10 manuscript.qmd

In @tbl-midline-params, we tabulate the mean and standard deviation of the sampled parameters. The bilateral model mostly reproduces the ipsilateral spread parameter values reported in the earlier publication on the unilateral model [@ludwig_modelling_2023]. Any discrepancies may be due to differences in the patient cohorts. Therefore, we omit the analysis of the ipsilateral spread patterns and focus instead on the analysis of contralateral involvement. The small contralateral spread parameters $b^c_v$ compared to the ipsilateral parameters $b^i_v$ adequately reflect the low prevalence of contralateral lymph node involvement for lateralized tumors. The mixing parameter $\alpha=$ {{< var model.params.mixing >}} describes that the probability of contralateral spread is higher for tumors extending over the mid-sagittal plane, but still lower than the probability for ipsilateral spread.

The high value of $t_{23}$ ({{< var model.params.IItoIII_spread >}}) compared to the value of $b_3$ ({{< var model.params.ipsi_TtoII_spread >}}) shows that the ipsilateral LNL III is rarely involved without the upstream involvement of LNL II.

>>>>

In @tbl-midline-params, we tabulate the mean and standard deviation of the sampled parameters. The bilateral model mostly reproduces the ipsilateral spread parameter values reported in the earlier publication on the unilateral model [@ludwig_modelling_2023]. Any discrepancies may be due to differences in the patient cohorts. Therefore, we omit the analysis of the ipsilateral spread patterns and focus instead on the analysis of contralateral involvement. The small contralateral spread parameters $b^c_v$ compared to the ipsilateral parameters $b^i_v$ adequately reflect the low prevalence of contralateral lymph node involvement for lateralized tumors. The mixing parameter $\alpha$ ({{< var model.params_percent.mixing >}}%) describes that the probability of contralateral spread is higher for tumors extending over the mid-sagittal plane, but still lower than the probability for ipsilateral spread.

The high value of $t_{23}$ ({{< var model.params_percent.IItoIII_spread >}}%) compared to the value of $b_3^\text{i}$ ({{< var model.params_percent.ipsi_TtoIII_spread >}}%) shows that the ipsilateral LNL III is rarely involved without the upstream involvement of LNL II.
